Forecasting the old-age dependency ratio to determine the best pension age

### 2020-05-05 PensionAge.Rmd
Now compiling

# Lower bound (starting at age 65)
pension_age_lower <- pension_age %>%
  filter(Policy == "Current", Year >= 2019) %>%
  select(-Policy)
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  while ((current > target) &
    (max(diff(pension_age_lower$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  }
}
# Mean (start at lower bound)
pension_age_optimal <- pension_age_lower
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  while ((current > target) &
    (max(diff(pension_age_optimal$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  }
}
# Upper bound (start at mean)
pension_age_upper <- pension_age_optimal
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  while ((current > target) &
    (max(diff(pension_age_upper$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  }
}
# Final results
OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
pension_age_optimal <- pension_age_optimal %>%
  mutate(
    Lo80 = pension_age_lower$Age,
    Hi80 = pension_age_upper$Age
  )
```

@@

```{r pensionagetables2, dependson="OADRat65"}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(
      trunc(Lo80), "Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
    ),
    AgeHi = paste0(
      trunc(Hi80), "Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Lo", "Hi"), 5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  )
kable_styling(kable_output, font_size = 7)
```

```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
## plots of OADR with plausible pension age schemes
OADR_optimal %>%
  ggplot(aes(x = Year)) +
  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
  autoplot(OADR.f.optimal$x) +
  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
  autolayer(OADR.f.optimal) +
  ggtitle("OADR forecast estimates for optimal pension ages") +
  xlab("year") +
  ylab("ratio")
```

```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
p1 <- autoplot(OADR.f.upper$x) +
  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
  autolayer(OADR.f.upper) +
  ggtitle("OADR for upper boundary pension ages") +
  xlab("Year") + ylab("ratio") +
  ylim(0.07, 0.27)
p2 <- autoplot(OADR.f.lower$x) +
  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
  autolayer(OADR.f.lower) +
  ggtitle("OADR for lower boundary pension ages") +
  xlab("Year") + ylab("ratio") +
  ylim(0.07, 0.27)
gridExtra::grid.arrange(p1, p2, ncol = 2)
```

```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade. The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
ggplot() +
  autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
  #  geom_hline(yintercept=65, color='black') +
  autolayer(ts(c(rep(65, 7), c(65.5, 65.5, 66.5, 66.5, 67, 67), rep(67, 37))[1:50],
    start = 2015
  ), series = "Approved change") +
  autolayer(ts(c(rep(65, 50)), start = 1990), series = "Pension age at 65") +
  xlab("Year") +
  ylab("Age of retirement")
```

>>>>

# Lower bound (starting at age 65)
pension_age_lower <- pension_age %>%
  filter(Policy == "Current", Year >= 2019) %>%
  select(-Policy)
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  while ((current > target) &
    (max(diff(pension_age_lower$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  }
}
# Mean (start at lower bound)
pension_age_optimal <- pension_age_lower
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  while ((current > target) &
    (max(diff(pension_age_optimal$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  }
}
# Upper bound (start at mean)
pension_age_upper <- pension_age_optimal
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  while ((current > target) &
    (max(diff(pension_age_upper$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  }
}
# Final results
OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
OADR_lower <- oadr_sim(aussim_df, pension_age_lower)
OADR_upper <- oadr_sim(aussim_df, pension_age_upper)
pension_age_optimal <- pension_age_optimal %>%
  mutate(
    Lo80 = pension_age_lower$Age,
    Hi80 = pension_age_upper$Age
  )
```

@@

```{r pensionagetables2, dependson="OADRat65", message=FALSE}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(
      trunc(Lo80), "Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
    ),
    AgeHi = paste0(
      trunc(Hi80), "Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Lo", "Hi"), 5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  ) %>%
  kable_styling(font_size = 7)
```

```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
## plots of OADR with plausible pension age schemes
OADR_optimal %>%
  ggplot(aes(x = Year)) +
  geom_hline(yintercept = target, col = "red") +
  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
  geom_line(aes(y=OADR), col="#0000cc") +
  geom_line(data=OADR_history, aes(y=OADR)) +
  ggtitle("OADR forecast estimates for optimal pension ages") +
  ylab("Old age dependency ratio") 
```

```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
bind_rows(
    OADR_upper %>% mutate(Series="Upper boundary"),
    OADR_lower %>% mutate(Series="Lower boundary"),
  ) %>%
  ggplot(aes(x = Year)) +
  geom_hline(yintercept = target, col = "red") +
  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
  geom_line(aes(y=OADR), col="#0000cc") +
  geom_line(data=OADR_history, aes(y=OADR)) +
  facet_grid(. ~ Series) +
  ggtitle("OADR forecasts for boundary pension age schemes") +
  ylab("Old age dependency ratio") 
```

```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade. The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
pension.fc <- structure(
  list(mean=ts(pension_age_optimal$Age, start=min(pension_age_optimal$Year)),
       lower=ts(pension_age_optimal$Lo80, start=min(pension_age_optimal$Year)),
       upper=ts(pension_age_optimal$Hi80, start=min(pension_age_optimal$Year)),
       level=80),
  class="forecast")
ggplot() +
  autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
  autolayer(
    ts(pension_age %>% filter(Policy=="Approved", Year >= 1995) %>% pull(Age), 
       start=1995), series = "Approved change"
  ) +
  autolayer(
    ts(pension_age %>% filter(Policy=="Current", Year >= 1995) %>% pull(Age), 
       start=1995), series = "Pension age at 65"
  )  +
  xlab("Year") + ylab("Age of retirement")
```
